\chapter{Aqademia's custom commands}

\section{\texttt{\textbackslash{}AqSetChapter}}

\begin{lstlisting}[language=Tex]
\AqSetChapter{Chapter~}
\end{lstlisting}

Sets the chapter's introductory string (\texttt{Chapter\~{}} by default).
The command's definition adds a whitespace (\texttt{\~{}}) after the argument string.

\section{\texttt{\textbackslash{}AqSetSection}}

\begin{lstlisting}[language=Tex]
\AqSetSection{\S}
\end{lstlisting}

Sets the section's introductory string (\texttt{\textbackslash{}S} by default).
The command's definition doesn't automatically add a whitespace (\texttt{\~{}}) after the argument string for more versatility, so it must be added at the end if required.

\section{\texttt{\textbackslash{}AqSetSubsection}}

\begin{lstlisting}[language=Tex]
\AqSetSubsection{}
\end{lstlisting}

Sets the subsection's introductory string (none by default).
The command's definition doesn't automatically add a whitespace (\texttt{\~{}}) after the argument string for more versatility, so it must be added at the end if required.

\section{\texttt{\textbackslash{}AqSetSubsubsection}}

\begin{lstlisting}[language=Tex]
\AqSetSubsubsection{}
\end{lstlisting}

Sets the subsubsection's introductory string (none by default).
The command's definition doesn't automatically add a whitespace (\texttt{\~{}}) after the argument string for more versatility, so it must be added at the end if required.

\section{\texttt{\textbackslash{}AqMaketitle}}

\begin{lstlisting}[language=Tex]
\AqMaketitle[author   = Atanasio Rubio Gil,
             cover    = cover,
             org      = University of GitHub,
             title    = Aqademia,
             subtitle = A fancy \LaTeX{} template,
             url      = https://github.com/Groctel/aqademia]
\end{lstlisting}

Generates a custom titlepage to substitute \texttt{\textbackslash{}maketitle}.
It displays \texttt{\textbackslash{}thetitle}, \texttt{\textbackslash{}theauthor} and \texttt{\textbackslash{}thedate} by default and can display the document's license it \texttt{doclicense} is loaded and a cover image if \texttt{graphicx} is loaded and the image is specified.

\pagebreak

It accepts the following key arguments:

\begin{center}
\begin{tabular}{l l l}
	\textbf{Key}      & \textbf{Default}                   & \textbf{Description}                                 \\
	\toprule
	\texttt{author}   & \texttt{\textbackslash{}theauthor} & Document's author.                                   \\
	\texttt{cover}    & \texttt{""}                        & Cover image name.                                    \\
	\texttt{org}      & \texttt{""}                        & Organisation shown above the title line.             \\
	\texttt{title}    & \texttt{\textbackslash{}thetitle}  & Document's title.                                    \\
	\texttt{subtitle} & \texttt{""}                        & Document's subtitle shown next to the title.         \\
	\texttt{url}      & \texttt{""}                        & Document's complementary url shown below the author. \\

\end{tabular}
\end{center}

By themselves, \texttt{\textbackslash{}theauthor} defaults to \texttt{Anonymous} and \texttt{\textbackslash{}thetitle}, to \texttt{Untitled document}.
